Quantitative processing of broadband data as implemented in a scientific splitbeam echosounder

### 2023-09-14 Paper/Supplementary.tex
Revert "Improve description for symbol u"
This reverts commit b93f5043c33068647469ddbdcd10471b89662f11.
Modification to Supplementary to match paper

$\hfl(\genidxsym,\stagesym)$ & & 1 & Complex valued receiving filter coefficients.\\
$\genidxsym$ & & 1 & Generic integer index.\\
$\Im(x)$ & & -- & The imaginary part of $x$.\\
$j$ & & & The square root of $-1$.\\
$\samplesymf$ & & 1 & Sample index in frequency domain.\\

@@

$\mysp(\samplesymt)$  & & dB re 1 $\textrm{m}^2$ & Point scattering strength.\\
$\sv$  & & dB re 1 $\textrm{m}^{-1}$ & Volume backscattering strength.\\
$\sv(\freqsym)$ & & dB re 1 $\textrm{m}^{-1}$ & Volume backscattering strength at frequency $\freqsym$.\\
$\sv(\samplesymt)$ & & dB re $\textrm{m}^{-1}$ & Volume backscattering strength at sample index $\samplesymt$.\\

@@

$\hannw$ & & 1 & The Hanning window function.\\
$\hannw(\genidxsym)$ & & 1 & The Hanning window function for index i, defined by $w(i) = 0.5(1+\cos (2\pi i /N_w)), -N_w/2 \leq i \leq N_w/2$.\\
$\hannwnorm(\genidxsym)$ & & 1 & Normalised Hanning window.\\

$x^*$ & & -- & The complex conjugate of $x$.\\
$||x||$ & & -- & The $l^2$-norm of $x$, also known as the Euclidean norm.\\

>>>>

$\hbp(\genidxsym,\stagesym)$ & & 1 & Complex valued receiving filter coefficients.\\
$\genidxsym$ & & 1 & Generic integer index.\\
$\Im(x)$ & & -- & The imaginary part of $x$.\\
$j$ & & & The square root of $-1$.\\
$\samplesymf$ & & 1 & Sample index in frequency domain.\\

@@

$\mysp(\samplesymt)$  & & dB re 1 $\textrm{m}^2$ & Point scattering strength.\\
$\sv$  & & dB re 1 $\textrm{m}^{-1}$ & Volume backscattering strength.\\
$\sv(\freqsym)$ & & dB re 1 $\textrm{m}^{-1}$ & Volume backscattering strength at frequency $\freqsym$.\\
$\sv(\samplesymt)$ & & dB re 1 $\textrm{m}^{-1}$ & Volume backscattering strength at sample index $\samplesymt$.\\

@@

$\hannw$ & & 1 & The Hann window function.\\
$\hannw(\genidxsym)$ & & 1 & The Hann window function for index i, defined by $w(i) = 0.5(1+\cos (2\pi i /N_w)), -N_w/2 \leq i \leq N_w/2$.\\
$\hannwnorm(\genidxsym)$ & & 1 & Normalised Hann window.\\

$x^*$ & & -- & The complex conjugate of $x$.\\
$||x||_2$ & & -- & The $l^2$-norm of $x$, also known as the Euclidean norm.\\
